Supplemental Materials, Methods and Results

### 2022-02-24 supp/Supplemental Materials and Methods.Rmd
updating script to run wth new file structure. Need to export from levelplot from functions to avoid conflict iwth ggplot2

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse, kableExtra, gridExtra, magrittr, Hmisc, googlesheets4, metafor, stringr, formatR, rmarkdown, kableExtra, flextable, raster, rasterVis, rnoaa, sp, ggmap, patchwork, ggpubr, RColorBrewer, sf, ggtree, ape, phytools, viridis, ncdf4.helpers, ncdf4, PCICt, readr, chron, microclima, NicheMapR, tmap, rgdal, MCMCglmm, brms, latex2exp)

@@

    #data <- read_sheet(ss = "q10_newdata")
    data <- read.csv("../../data/CombinedData_wide.csv", stringsAsFactors = FALSE)
    data$lat <- as.numeric(data$lat)
    new_papers <- data[-grep("_o", data$record_num),]
    old_papers <- data[grep("_o", data$record_num),]

@@

      #write.csv(data, file = "./output/data/data_final_wide.csv", row.names = FALSE)
##################################
## Re-organise the data frame
##################################

@@

      # Checks:
      dim(data_long)
      with(data_long, table(type)) # Acute should be 2x larger
      with(data_long, table(type, trait_category))
      #write.csv(data_long, file = "./output/data/data_final_long.csv", row.names = FALSE)
```

@@

grid   = expand.grid(lon = lon, lat = lat)
#cutpts = c(-5, -2, 0, 5, 10, 15, 20, 25, 30, 35)
levelplot(sst.slice ~ lon * lat, data = grid,  cuts = 11, pretty = TRUE, 
          col.regions = colfunc(50), ylab = "Latitude", xlab = "Longitude")  +# Have a quick look
          layer(sp.points(points, pch = 16, col = "black")) + 
          layer(sp.lines(coast_outline, col="black", lwd=0.5))

@@

 p1 <- levelplot(seasonalityDec/10, margin =FALSE, cuts=20, pretty=TRUE, main = "December", col.regions=colfunc(50)) +
        layer(sp.points(points, pch = 16, col = "black")) +
        layer(sp.lines(coast_outline, col="black", lwd=0.5)) # Add coastline layer to define boundaries better +
 p2 <- levelplot(seasonalityApril/10, margin =FALSE, main = "April", cuts=20, pretty=TRUE, col.regions=colfunc(50)) + 
        layer(sp.points(points, pch = 16, col = "black")) + 
        layer(sp.lines(coast_outline, col="black", lwd=0.5)) # Add coastline layer to define boundaries better
 p3 <- levelplot(seasonalityAugust/10, margin =FALSE, main = "August",cuts=20, pretty=TRUE, col.regions=colfunc(50)) +
        layer(sp.points(points, pch = 16, col = "black")) + 
        layer(sp.lines(coast_outline, col="black", lwd=0.5)) # Add coastline layer to define boundaries better
 p4 <- levelplot(seasonalityAugust/10, margin =FALSE, main = "August",cuts=50, pretty=TRUE, 
                 col.regions=colfunc(100), ylim = c(0,100), xlim = c(-130, -40)) + 
        layer(sp.points(points, pch = 16, col = "black")) + 
        layer(sp.lines(coast_outline, col="black", lwd=0.5)) # Add coastline layer to define boundaries better

@@

rerun1 = FALSE
if(rerun1){
  lnRR_Q10_mod1 <- brm(lnRR_Q10 | se(sqrt(V_lnRR_Q10)) ~ type + (1 + type|paper) + (1|species_full) + (1|obs), family = gaussian(), data = data_long, control = list(adapt_delta = 0.95), cores = 4, chains = 4, iter = 4000, warmup = 1000, thin = 5)
  saveRDS(lnRR_Q10_mod1, "../models/lnRR_Q10_mod1")
} else{
lnRR_Q10_mod1 <- readRDS("../models/lnRR_Q10_mod1")  }

@@

rerun2 = FALSE
if(rerun2){
  lnRR_Q10_mod2 <- brm(lnRR_Q10 | se(sqrt(V_lnRR_Q10)) ~ type*habitat + (1 + type|paper) + (1|species_full) + (1|obs), family = gaussian(), data = data_long, control = list(adapt_delta = 0.99), cores = 4, chains = 4, iter = 4000, warmup = 1000, thin = 5)
  saveRDS(lnRR_Q10_mod2, "../models/lnRR_Q10_mod2")
}else{
  lnRR_Q10_mod2 <- readRDS("../models/lnRR_Q10_mod2")
}
# Checks
 summary(lnRR_Q10_mod2) # Rhat all 1 = chain convergence
    plot(lnRR_Q10_mod2) # Good mixing
   pairs(lnRR_Q10_mod2) # Looks good
bayes_R2(lnRR_Q10_mod2) # Variance explained by model

>>>>

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse, kableExtra, gridExtra, magrittr, Hmisc, googlesheets4, metafor, stringr, formatR, rmarkdown, kableExtra, flextable, raster, rasterVis, rnoaa, sp, ggmap, patchwork, ggpubr, RColorBrewer, sf, ggtree, ape, phytools, viridis, ncdf4.helpers, ncdf4, PCICt, readr, chron, tmap, rgdal, MCMCglmm, brms, latex2exp)

@@

    #data <- read_sheet(ss = "q10_newdata")
    data <- read.csv("../data/CombinedData_wide.csv", stringsAsFactors = FALSE)
    data$lat <- as.numeric(data$lat)
    new_papers <- data[-grep("_o", data$record_num),]
    old_papers <- data[grep("_o", data$record_num),]

@@

      write.csv(data, file = "../output/data/data_final_wide.csv", row.names = FALSE)
##################################
## Re-organise the data frame
##################################

@@

      # Checks:
      dim(data_long)
      with(data_long, table(type)) # Acute should be 2x larger
      with(data_long, table(type, trait_category))
      write.csv(data_long, file = "../output/data/data_final_long.csv", row.names = FALSE)
```

@@

grid   = expand.grid(lon = lon, lat = lat)
#cutpts = c(-5, -2, 0, 5, 10, 15, 20, 25, 30, 35)
levelplot(sst.slice ~ lon * lat, data = grid,  cuts = 11, pretty = TRUE, 
          col.regions = colfunc(50), ylab = "Latitude", xlab = "Longitude")  +# Have a quick look
          latticeExtra::layer(sp.points(points, pch = 16, col = "black")) + 
          latticeExtra::layer(sp.lines(coast_outline, col="black", lwd=0.5))

@@

 p1 <- levelplot(seasonalityDec/10, margin =FALSE, cuts=20, pretty=TRUE, main = "December", col.regions=colfunc(50)) +
        latticeExtra::layer(sp.points(points, pch = 16, col = "black")) +
        latticeExtra::layer(sp.lines(coast_outline, col="black", lwd=0.5)) # Add coastline layer to define boundaries better +
 p2 <- levelplot(seasonalityApril/10, margin =FALSE, main = "April", cuts=20, pretty=TRUE, col.regions=colfunc(50)) + 
        latticeExtra::layer(sp.points(points, pch = 16, col = "black")) + 
        latticeExtra::layer(sp.lines(coast_outline, col="black", lwd=0.5)) # Add coastline layer to define boundaries better
 p3 <- levelplot(seasonalityAugust/10, margin =FALSE, main = "August",cuts=20, pretty=TRUE, col.regions=colfunc(50)) +
        latticeExtra::layer(sp.points(points, pch = 16, col = "black")) + 
        latticeExtra::layer(sp.lines(coast_outline, col="black", lwd=0.5)) # Add coastline layer to define boundaries better
 p4 <- levelplot(seasonalityAugust/10, margin =FALSE, main = "August",cuts=50, pretty=TRUE, 
                 col.regions=colfunc(100), ylim = c(0,100), xlim = c(-130, -40)) + 
        latticeExtra::layer(sp.points(points, pch = 16, col = "black")) + 
        latticeExtra::layer(sp.lines(coast_outline, col="black", lwd=0.5)) # Add coastline layer to define boundaries better

@@

rerun1 = FALSE
if(rerun1){
  lnRR_Q10_mod1 <- brm(lnRR_Q10 | se(sqrt(V_lnRR_Q10)) ~ type + (1 + type|paper) + (1|species_full) + (1|obs), family = gaussian(), data = data_long, control = list(adapt_delta = 0.95), cores = 4, chains = 4, iter = 4000, warmup = 1000, thin = 5)
  saveRDS(lnRR_Q10_mod1, "../output/models/lnRR_Q10_mod1")
} else{
lnRR_Q10_mod1 <- readRDS("../output/models/lnRR_Q10_mod1")  }

@@

rerun2 = FALSE
if(rerun2){
  lnRR_Q10_mod2 <- brm(lnRR_Q10 | se(sqrt(V_lnRR_Q10)) ~ type*habitat + (1 + type|paper) + (1|species_full) + (1|obs), family = gaussian(), data = data_long, control = list(adapt_delta = 0.99), cores = 4, chains = 4, iter = 4000, warmup = 1000, thin = 5)
  saveRDS(lnRR_Q10_mod2, "../output/models/lnRR_Q10_mod2")
}else{
  lnRR_Q10_mod2 <- readRDS("../output/models/lnRR_Q10_mod2")
}
# Checks
 summary(lnRR_Q10_mod2) # Rhat all 1 = chain convergence
    plot(lnRR_Q10_mod2) # Good mixing
   pairs(lnRR_Q10_mod2) # Looks good
bayes_R2(lnRR_Q10_mod2) # Variance explained by model
